% !TEX root = ./zeth-protocol-specification.tex

\chapter*{Change log}\label{chap:change-log}
% ventry format:
%\vhentry{Semantic version: X.Y}{Date: DD.MM.YYY}{Github handle: XX}{Version msg}
%\begin{versionhistory}
%    \vhentry{0.1}{04.12.2019}{AntoineRondelet}{Creation of the document}
%\end{versionhistory}
\begin{itemize}
    \item \textbf{Version:} 0.0, \textbf{Date:} 04/12/2019, \textbf{Contributor:} Antoine Rondelet, \textbf{Description:} Creation of the document. Established initial table of content and started to populate sections with bullet lists to develop in further versions of the document.
    \item \textbf{Version:} 0.1, \textbf{Date:} 20/12/2019, \textbf{Contributor:} Antoine Rondelet, \textbf{Description:} Refactored the structure of the document. Finalized the table of content, wrote sections on notations and preliminaries, and introduced the content related to the malleability fix.
    \item \textbf{Version:} 0.2, \textbf{Date:} 24/02/2020, \textbf{Contributor:} Clearmatics Cryptography R\&D, \textbf{Description:}
        \begin{itemize}
            \item \textbf{Date:} 26/02/2020, \textbf{Contributor:} Duncan Tebbs, \textbf{Description:} Wrote section on wallet implementation and side-channel attacks considerations.
            \item \textbf{Date:} 02/03/2020, \textbf{Contributor:} Giuseppe Giffone, \textbf{Description:} Changed Merkle tree hash function to MiMC compression function.
            \item \textbf{Date:} 04/03/2020, \textbf{Contributor:} Duncan Tebbs, Michal Zajac, \textbf{Description:} Added background on Groth16 SNARK and SNARK scheme instantiation in the protocol.
            \item \textbf{Date:} 04/03/2020, \textbf{Contributor:} Raphael Toledo, \textbf{Description:} Wrote section on the packing policy and corresponding attack.
            \item \textbf{Date:} 04/03/2020, \textbf{Contributor:} Duncan Tebbs, \textbf{Description:} Refactored the data structures preliminary section.
            \item \textbf{Date:} 24/03/2020, \textbf{Contributor:} Raphael Toledo, \textbf{Description:} Changed the PRF and commitment instantiation with Blake2s compression function.
            \item \textbf{Date:} 17/04/2020, \textbf{Contributor:} Giuseppe Giffone, \textbf{Description:} Added DHAES encryption scheme.
        \end{itemize}
    \item \textbf{Version:} 0.3, \textbf{Date:} 09/06/2020, \textbf{Contributor:} Antoine Rondelet, \textbf{Description:} Fixed various inconsistencies throughout the document (notational mistakes in document body and in proofs, latex macros, and typos).
    \item \textbf{Version:} 1.0, \textbf{Date:} 30/06/2020, \textbf{Contributor:} Antoine Rondelet, Duncan Tebbs, Michal Zajac, \textbf{Description:} Global review of the document: fixed inconsistencies in definitions and notations, corrected grammatical mistakes and typos, added examples, figures and merged sections 5 and 6 of Chapter 1 for clarity, added missing references.
    \item \textbf{Version:} 1.1, \textbf{Date:} 06/11/2020, \textbf{Contributor:} Duncan Tebbs, \textbf{Description:} Specification in terms of a generic curve, with constants provided for \BNCurve and \BLSCurve. Some clarification and grammar fixes.
    \item \textbf{Version:} 1.2, \textbf{Date:} 27/01/2021, \textbf{Contributor:} Antoine Rondelet, Michal Zajac, \textbf{Description:} Fix erroneous prime fields used in data types, added elliptic curve group notations, fixed erroneous Groth16 formulas and notation inconsistencies between group and field elements.
\end{itemize}
