% !TEX root = ../zeth-protocol-specification.tex

\chapter{Instantiation of the cryptographic primitives}\label{chap:instantiation}

In this chapter, we start by instantiating the cryptographic building blocks used in previous sections to describe the \zeth~\dapscheme~design. Finally, we proceed by providing security proofs justifying that our instantiation complies with the security requirements listed in previous sections.

Note that, in several cases, it is necessary to specify details in terms of concrete properties of the curve \Curve~and associated scalar field $\FFx{\rCURVE}$. In these cases, we focus on two curves of interest: \BNCurve~and \BLSCurve. We note, however, that other suitable curves could be used.

\BNCurve~\cite{bn-prime} has several properties that make it implementation-friendly. Elements of both the base field and scalar field can be represented in \ethWordLen~bits (the native word size of the \evm), allowing efficient encoding and manipulation of such elements. Moreover, a subset of operations on \BNCurve are supported by the \evm~through precompiled contracts. These precompiled contracts enable verification of signatures (\cref{instantiation:otsig}) and zero-knowledge proofs (\cref{instantiation:zksnark}), required by this protocol, with minimal gas overhead.

\BLSCurve~\cite{bowe18zexe}, like \BNCurve, has the advantage that scalar field elements can be represented within \ethWordLen-bit words (although the same is not true of base field elements). However, the \evm~provides no native support for \BLSCurve, which increases the complexity of the \mixer~implementation (see \cref{zeth-protocol:process-tx}~for details of the operations to be performed). An advantage that \BLSCurve does provide, is that is it the ``inner'' curve of a one-layer chain (as described in \cite{bowe18zexe,housni2020onelayer}). Therefore zero-knowledge proofs using \BLSCurve can be efficiently verified by statements in other zero-knowledge proofs using an approporiate ``outer'' pairing. Support for \BLSCurve in \zeth~therefore admits several applications (no explicitly covered by this document), such as aggregation of proofs over multiple \zeth~transactions (e.g.~\cite{rondelet2020zecale}).

Further details related to implementation and optimization are given in \cref{chap:implementation}.

\input{./chapters/chap03-sec01.tex} % PRFs, COMM and CRHs (may need to be split if we decide to instantiate these with different functions)
\input{./chapters/chap03-sec02.tex} % MKHASH
\input{./chapters/chap03-sec03.tex} % Zeth statement after instantiation
\input{./chapters/chap03-sec04.tex} % OT-SIG
\input{./chapters/chap03-sec05.tex} % Encryption scheme
\input{./chapters/chap03-sec06.tex} % ZkSNARK
